---
title: "Homework 5"
author: "Salah El-Sadek (sne2114)"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

```{r}
homicide_data = read_csv("./homicide-data.csv")
```


This is data on over 50,000 homicides across 50 large cities in the U.S. collected by the Washington Post.
There are `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns overall.\
Variables in the data include: ***`r names(homicide_data)`***

Next, we create a city_state variable using data on city and state.
```{r}
homicide_df = 
  homicide_data %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")

homicide_df
```

Here we obtain the total number of homicides and total number of unsolved homicides (no arrest made).

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

aggregate_df
```

Using prop.test to estimate proportion of homicides that went unsolved in Baltimore, MD.

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

Iterating the prop.test for all cities.

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

results_df
```

Plotting the proportion of unsolved homicides with error bars for each city.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```





<!-- ## Problem 2 ideas ... -->


<!-- import one dataset  -->

<!-- ```{r} -->
<!-- data_1 = read_csv("lda_data/con_01.csv") -->
<!-- ``` -->

<!-- ```{r, error = TRUE} -->
<!-- path_df =  -->
<!--   tibble( -->
<!--     path = list.files("lda_data"), -->
<!--   ) %>%  -->
<!--   mutate( -->
<!--     path = str_c("lda_data/", path), -->
<!--     data = map(.............)) -->
<!-- read_csv(path_df$path[[1]]) -->
<!-- ``` -->

